\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\hypersetup{
	colorlinks   = true,    % Colours links instead of ugly boxes
	urlcolor     = blue,    % Colour for external hyperlinks
	linkcolor    = blue,    % Colour of internal links
	citecolor    = red      % Colour of citations
}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Abhay Charan} % Your name
\address{D-1025 \\ Bindapur D.D.A Flats , N.D. 110059} 
\address{(+91)~8826403904 \\ abhaycharan13@gmail.com} % Your phone number and email 

\begin{document}
	\centering{ Github : 
		\url{https://www.github.com/13abhay/}}
	\\
	\centering{Linkedin Profile : 
\url{https://www.linkedin.com/in/abhay-charan-139890122/}}
%----------------------------------------------------------------------------------------

%   Objective
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
To apply and expand my knowledge and skill set to real-world situations, in a demanding environment which allows me to enhance and develop my all-round skills and abilities.
\end{rSection}

%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Jamia Millia Islamia} \hfill {\em 2015 - Present} 
\\ B.Tech (Computer Engineering) \hfill { Overall CPI: 7.79/10 (Upto 6th Sem)} 
\\{\bf Kendriya Vidyalaya Janak Puri} \hfill {\em 2014 and 2012} \\
12th and 10th \hfill {87.4\% and 9.4/10}
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  C/C++, Python, Java, MATLAB, Shell Scripting(Bash) \\ \\
Industry Skills & \textbullet \ Machine Learning \textbullet \ Deep Learning \textbullet \ Web Development\\&
\textbullet \ Robotics \textbullet \ Drone  Mechanics \textbullet \ Signal \& Image Processing \\& \textbullet \ Basics of Ethical Hacking and Pentesting
% Android App Development
\\ \\
Other Skills & \textbullet \ EEG \textbullet \ fMRI \textbullet \ Basics of Cognitive Sciences and Brain Psychology 
\\ \\
Academic Courses & \textbullet \ Data Structures and Algorithms \textbullet \ DBMS \textbullet \ Networking\\
& \textbullet \ Cryptography \textbullet \ Microprocessor \textbullet \ Operating System\\ & \textbullet \ Automata Theory \textbullet \ Compiler Design \textbullet \ Computer Organization\\ & \textbullet \ Computer Architecture \textbullet \ System Software \textbullet \ Analog \& Digital
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Institute of Nuclear Medicine \& Allied Sciences, DRDO}{June 2018 - July 2018}{Intern}{}
\item Worked on evaluation of different Machine Learning models for EEG Microstates Estimation.
\item Learned about fMRI,EEG,simultaneous EEG-fMRI and their processing.
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Cortex Logic(South African Startup)}{October 2017 - October 2017}{Web User Interface Developer(Remote)}{}
\item Worked in a team of 3 people for an AI Search Tool Project
\item Connected the back-end application to front-end using MongoDB and Django where front-end was designed in Django Template Language(DTL).
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{The Student Hub(South African Startup)}{July 2017 - August 2017}{System Developer(Remote)}{}
	\item Worked on building an educational platform (www.eraonline.co.za)
	\item Used Symfony framework, MYSQL and many core web development tools.
	\item Added many features in the project like automatic E-Mail/SMS sender
	whenever professor publishes new test. Fixed many previous bugs also.
\\	
\end{rSubsection}

\end{rSection}


%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Co-Curricular Activities} \itemsep -2pt
\item \textbullet \ 3rd position holder (National) in E-yantra Robotics Competition(IIT BOMBAY)
in Theme Chaser Drone.
\item \textbullet \ Participated in Smart India Hackathon 2018 Grand Finale in project of anomaly as Team Leader.
detection in ship trajectories.
\item \textbullet \ Made a Fighting Robot with roller embedded with blades as weapon(team of 4).
\item \textbullet \ Made an E-commerce Website and Railway Reservation System(Web).
\item \textbullet \ Silver medal in International Mathematics Olympiad by Amity University.
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} \itemsep -3pt
	\item \textbullet \ Basketball (Runner-ups) (4th sem) in inter department college competition.
	\item \textbullet \ Volunteer for Brain Research Experiments at INMAS.
	\item \textbullet \ Penning quotes and poetry
	\item \textbullet \ Basic Spanish Language(Learning).
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Soft Skills}
  \itemsep -3pt
 \item \textbullet \ Quick learning and grasping ability
 \item \textbullet \ Co-operative and adjustable nature
 \item \textbullet \ Good Analytical and Logical skills 
 \item \textbullet \ Initiator and passionate about working and learning new things 
 \item \textbullet \ Strong believer and hardworking
\end{rSection}



\end{document}

              